An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-15 paper/paper.tex
Paper: write "Language and Tools" section of "Implementation", and fix a typo

For every file a peer wishes to backup, it must find a predetermined number of nodes that can store the file. To ensure an even distributionof responsibility in the structured overlay network, a random bitstring in the address space of the overlay network is generated. The DHT provides the functionality to find the node whose ID is \texit{closest} to the randomly generated bitstring. The peer then gets the metadata record for the node from the DHT. From the metadata record, the peer can calculate if the node is \textit{obligated} to store its file. We discuss the situation in which a node is obligated to store a peers file in section \ref{sec:Fairness}. The peer also uses the metadata record to ensure the node does not have too many blacklisters. If the node meets both requirements, the peer uses the data layer to contact the node to inform it of the decision. The metadata layer is updated appropriately, and the data layer is used to transfer the file. This process repeats until the predetermined number of nodes are found.

@@

\chapter{Implementation} \label{chap:impl}
\section{Language and Tools}
% C++
% Boost
% Jsoncpp - serialization for message passing (BTSync uses it too)
% cURLpp

Our implementation of BTBackup is written in C++.

>>>>

For every file a peer wishes to backup, it must find a predetermined number of nodes that can store the file. To ensure an even distributionof responsibility in the structured overlay network, a random bitstring in the address space of the overlay network is generated. The DHT provides the functionality to find the node whose ID is \textit{closest} to the randomly generated bitstring. The peer then gets the metadata record for the node from the DHT. From the metadata record, the peer can calculate if the node is \textit{obligated} to store its file. We discuss the situation in which a node is obligated to store a peers file in section \ref{sec:Fairness}. The peer also uses the metadata record to ensure the node does not have too many blacklisters. If the node meets both requirements, the peer uses the data layer to contact the node to inform it of the decision. The metadata layer is updated appropriately, and the data layer is used to transfer the file. This process repeats until the predetermined number of nodes are found.

@@

\chapter{Implementation} \label{chap:impl}

Our goals for the implementation of BTBackup were that it is fast, modular, platform independent, and as close to the specification as time permitted. Furthermore, it should allow us to adequately analyze the feasibility and performance of BitTorrent Sync as the data transport protocol in the backup system.

\section{Language and Tools}

Our implementation of BTBackup is written in C++. This language was primarily chosen for its speed. We use the Boost library (version 1.55) to remain platform independent. We use Jsoncpp (version 0.6.0-rc2) to serialize and unserialize the JSON that the implementation uses for message passing. We use cURLpp (version 0.7.3) to interface with the BitTorrent Sync Web API.
